Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-03-19 AppendixB-EField/B-LArIATEField.tex
Changing organization structure

\chapter{Measurement of LArIAT Electric Field}{ch:AppendixA}
The electric field of a LArTPC in the drift volume is a fundamental quantity for the proper functionality of this technology, as it affects almost every reconstructed quantity such as the position of hits or their collected charge. Given its importance, we calculate the electric field for LArIAT with a single line diagram from our HV circuit and we cross check the obtained value with a measurement relying only on TPC data.

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.45]{./AppentixA-EField/Images/Walkowiak.png}\\
\caption{Drift velocity dependence on electric field for several temperatures. The slope of the line at any one point represents the electron mobility for that given temperature and electric field.}
\label{fig:EV}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=3in]{AppentixA-EField/Images/CircuitLArIAT.png}
\caption{\textcolor{red}{get rid of current line} LArIAT HV simple schematics.}
\label{fig:circuit}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=3in]{AppentixA-EField/Images/glassman_current_20160525-30.png}
\caption{\textcolor{red}{the axis is wrong!!} Current reading from the Glassman between May 25th and May 30th, 2016 (typical Run-II conditions).}
\label{fig:currentMeasurement}
\end{minipage}
\end{figure}

@@

\subsection*{E field using cathode-anode piercing tracks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b]
\centering
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=3in]{AppentixA-EField/Images/TPCCrossSectionView.png}
\caption{Pictorial representation of the YX view of the TPC. The distance within the anode planes and between the shield plane and the cathode is purposely out of proportion to illustrate the time difference between hits on collection and induciton. A ACP track is shown as an example.}
\label{fig:Scheme}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=3in]{AppentixA-EField/Images/AngleDef.png}
\caption{Angle definition in the context of LArIAT coordinates system.}
\label{fig:AngleDef}
\end{minipage}
\end{figure}
We devise an independent method to measure the drift time (and consequently drift velocity and electric field) using TPC cathode to anode piercing tracks. We use this method as a cross check to the single line method.
The basic idea is simple:
\begin{itemize}
\item[0.] Select cosmic ray events with only 1 reconstructed track 
\item[1.] Reduce the events to the one contaoning tracks that cross both anode and cathode
\item[2.] Identify the first and last hit of the track
\item[3.] Measure the time difference between these two hits ($\Delta t$).
\end{itemize}
This method works under the assumptions that the time it takes for a cosmic particle to cross the chamber ($\sim$ns) is small compared to the charge drift time ($\sim$ hundreds of $\mu$s).

@@

\begin{figure}[h!]
\begin{minipage}{0.40\textwidth}
\centering
\includegraphics[width=3in]{AppentixA-EField/Images/RunIIPosCol.png}
\caption{Collection plane $\Delta$t fit for Run II positive polarity ACP data  selected tracks.}
\label{fig:Run2PosColFit}
\end{minipage}\hfill
\begin{minipage}{0.40\textwidth}
\centering
\includegraphics[width=3in]{AppentixA-EField/Images/RunIIPosInd.png}
\caption{Induction plane $\Delta$t fit for Run II positive polarity ACP data  selected tracks.}
\label{fig:Run2PosIndFit}
\end{minipage}
\end{figure}

>>>>

\chapter{Measurement of LArIAT Electric Field}{ch:AppendixB}
The electric field of a LArTPC in the drift volume is a fundamental quantity for the proper functionality of this technology, as it affects almost every reconstructed quantity such as the position of hits or their collected charge. Given its importance, we calculate the electric field for LArIAT with a single line diagram from our HV circuit and we cross check the obtained value with a measurement relying only on TPC data.

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.45]{./AppendixB-EField/Images/Walkowiak.png}\\
\caption{Drift velocity dependence on electric field for several temperatures. The slope of the line at any one point represents the electron mobility for that given temperature and electric field.}
\label{fig:EV}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=3in]{AppendixB-EField/Images/CircuitLArIAT.png}
\caption{\textcolor{red}{get rid of current line} LArIAT HV simple schematics.}
\label{fig:circuit}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=3in]{AppendixB-EField/Images/glassman_current_20160525-30.png}
\caption{\textcolor{red}{the axis is wrong!!} Current reading from the Glassman between May 25th and May 30th, 2016 (typical Run-II conditions).}
\label{fig:currentMeasurement}
\end{minipage}
\end{figure}

@@

\subsection*{E field using cathode-anode piercing tracks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b]
\centering
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=3in]{AppendixB-EField/Images/TPCCrossSectionView.png}
\caption{Pictorial representation of the YX view of the TPC. The distance within the anode planes and between the shield plane and the cathode is purposely out of proportion to illustrate the time difference between hits on collection and induciton. A ACP track is shown as an example.}
\label{fig:Scheme}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=3in]{AppendixB-EField/Images/AngleDef.png}
\caption{Angle definition in the context of LArIAT coordinates system.}
\label{fig:AngleDef}
\end{minipage}
\end{figure}
We devise an independent method to measure the drift time (and consequently drift velocity and electric field) using TPC cathode to anode piercing tracks. We use this method as a cross check to the single line method.
The basic idea is simple:
\begin{itemize}
\item[0.] Select cosmic ray events with only 1 reconstructed track 
\item[1.] Reduce the events to the one contaoning tracks that cross both anode and cathode
\item[2.] Identify the first and last hit of the track
\item[3.] Measure the time difference between these two hits ($\Delta t$).
\end{itemize}
This method works under the assumptions that the time it takes for a cosmic particle to cross the chamber ($\sim$ns) is small compared to the charge drift time ($\sim$ hundreds of $\mu$s).

@@

\begin{figure}[h!]
\begin{minipage}{0.40\textwidth}
\centering
\includegraphics[width=3in]{AppendixB-EField/Images/RunIIPosCol.png}
\caption{Collection plane $\Delta$t fit for Run II positive polarity ACP data  selected tracks.}
\label{fig:Run2PosColFit}
\end{minipage}\hfill
\begin{minipage}{0.40\textwidth}
\centering
\includegraphics[width=3in]{AppendixB-EField/Images/RunIIPosInd.png}
\caption{Induction plane $\Delta$t fit for Run II positive polarity ACP data  selected tracks.}
\label{fig:Run2PosIndFit}
\end{minipage}
\end{figure}

### 2018-03-19 Chapter-2/2-LArTPCs.tex
Changing organization structure

\chapter{Liquid Argon Detectors at the Intensity Frontier}\label{ch:1}
Following the recommendation of the latest Particle Physics Project Prioritization Panel  \cite{ParticlePhysicsProjectPrioritizationPanel(P5):2014pwa}, the US is dedicating substantial resources to the development of a short- and long- baseline neutrino program to address the fundamental questions in neutrino physics today. A large portion of this program pivots on the Liquid Argon Time Projection Chamber (LArTPC) detector technology. In the next few years, LArTPC experiments -- such as the Short-Baseline Neutrino program (SBN) and DUNE -- will be major players in the intensity frontier field.

\section{The SBN Program}
\subsection{SBN Goals}
\subsection{Neutrino Interactions and Detection }

\section{DUNE}
\subsection{DUNE Non-Accelerator Physics Program}
\subsection{Rare Decay Searches: Experimental Limit}
\subsection{Nucleon Decay Detection in LAr}

@@

\subsection{Time Projection Chamber}
\subsection{Ionization Detectors with Noble Liquids}
\subsection{LArTPC: Principles of Operation}
\subsection{Liquid Argon Ionization Charge Detection}
\subsubsection{Electron Life Time \& purity}
\subsubsection{Space Charge Effect}
\subsubsection{Recombination Effect}
\subsection{Liquid Argon scintillation Light Detection}
\subsubsection{LAr Scintillation Process}
\subsubsection{Wavelength Shifting of LAr Scintillation Light}

>>>>

\chapter{Liquid Argon Detectors at the Intensity Frontier}\label{ch:1}

In the next few years, LArTPC experiments -- such as the Short-Baseline Neutrino program (SBN) and DUNE -- will be major players in the intensity frontier field.

@@

\subsection{Time Projection Chamber}
\subsection{Ionization Detectors with Noble Liquids}
\subsection{LArTPC: Principles of Operation}
\subsection{Liquid Argon Ionization Charge Detection}
\subsubsection{Electron Life Time \& purity}
\subsubsection{Space Charge Effect}
\subsubsection{Recombination Effect}
\subsection{Liquid Argon scintillation Light Detection}
\subsubsection{LAr Scintillation Process}
\subsubsection{Wavelength Shifting of LAr Scintillation Light}
\section{The SBN Program: Neutrino Interaction and Detection}
%\subsection{SBN Goals}
%\subsection{Neutrino Interactions and Detection }
\section{DUNE: Rare Decay Searches}
%\subsection{Non-Accelerator Physics Program}
%\subsection{Rare Decay Searches: Experimental Limit}
%\subsection{Nucleon Decay Detection in LAr}
\section{Enabling the next generation of discoveries: LArIAT}

### 2018-03-19 Chapter-3/3-TheLArIATExperiment.tex
Changing organization structure

%\begin{comment}     
\begin{figure}
  \centering  	
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-2/Images/AcceleratorFNAL.png}
\label{fig:Accelerator}
\caption{Layout of Fermilab Acellerator complex.}
\end{figure}

%\begin{comment}     
\begin{figure}
  \centering  	
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-2/Images/Tertiary.png}
\label{fig:tert-layout}
\caption{Birds eye view of the LArIAT tertiary beamline. In grey: upstream and downstream collimators; in yellow: bending magnets in yellow; in red: wire chambers; in blue: time of flight; in green: liquid argon TPC volume; in maroon: muon range statck.}
\end{figure}

@@

\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=3.0in]{Chapter-2/Images/ExcitationCurves.png}
\caption{
{ Magnetic field over current as a function of the current, for one NDB magnet (excitation curve). The data was collected using two Hall probes (blue and green). We fit the readings with a cubic function (black) to average of measurements (red) given in the legend.}
}
\label{fig:magnet_excitation}
\end{centering}
\end{figure}

@@

\subsection{Multi-Wire Proportional Chambers}\label{sec:MWPC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=2.3in]{Chapter-2/Images/WireChamber.png}
\caption{
{One of the four Multi Wire Proportional Chambers (WC) used in the LArIAT tertiary beamline.}
}
\label{fig:wirechamber}
\end{centering}
\end{figure}

@@

%\begin{figure}[!h]
%\begin{centering}
%\vspace{-0.3cm}
%\includegraphics[height=2.3in]{Chapter-2/Images/tofdelay.png}
%\caption{
%{\scriptsize \sf Pictures of the TOF system as was deployed during Run-I and Run-II data taking. The left image is of the upstream TOF paddle and the right image is of the downstream TOF paddle }
%}
%\label{fig:TOFSystemRunIandII}
%\end{centering}
%\end{figure}

@@

\begin{figure}[h!]
\centering
 \includegraphics[angle=90,width=0.7\textwidth]{Chapter-2/Images/Cosmic_Paddle.jpg}
\caption{Photograph of one of the scintillation counters used in the cosmic towers. } 
\label{pic:cosmicpaddle}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.18]{Chapter-2/Images/Cryostat1.jpg}
\includegraphics[scale=0.07]{Chapter-2/Images/Cryostat2.jpg}
\caption{\emph{(left)} The LArIAT cryostat open with the TPC placed in the inner volume. \emph{(right)} The LArIAT cryostat fully sealed during initial commissioning prior to installation at Fermilab Testbeam Facility.Access to the internal volume is possible by opening the upstream end caps of the inner and outer vessels. }
\label{fig:LArIATCryoStat}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{Chapter-2/Images/CryoMods.png}
\caption{Pictures of the modified components of the cryostat. $1)$ The addition of an outlet to the bottom of the cryostat to allow connections to the purification system; $2)$ The ``beam-window'' on the outer endcap and the concave inner surface of the inner endcap (referred to as the excluder) to reduce the amount of material through which beam particles must travel before entering the TPC; $3)$ The modified side port for the LArIAT light collection system.}
\label{fig:LArIATCryoMods}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{Chapter-2/Images//HVSchematic.png}\\
\caption{Schematic of the LArIAT high voltage system.}
\label{fig:HVScheme}
\end{figure}%See DocDB 1472

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{Chapter-2/Images/DriftRegions.png}\\
\caption{Schematic of the three drift regions inside the LArIAT TPC: the main drift volume between the cathode and the shield plane (C-S) in green, the region between the shield plane and the induction plane (S-I) in purple, and the region between the induction plane and the collection plane (I-C) in pink.}
\label{fig:driftregions}
\end{figure}

@@

\begin{figure}[htbp]
 \centering
 \includegraphics[width=1.0\textwidth]{Chapter-2/Images/LArIAT_FE_Electronics.png}
\caption{Overview of LArIAT Front End electronics. } 
\label{pic:FEelectronics}
\end{figure}

@@

%------------------------------------------
\begin{figure}
\centering
\includegraphics[height=2.2in]{Chapter-2/Images/lightsys_pmts.png}
\hspace{1cm}
\includegraphics[height=2.2in]{Chapter-2/Images/lightsys_wls.png}
\caption{LArIAT's photodetector system for observing LAr scintillation light inside the TPC (left), and a simplified schematic of VUV light being wavelength-shifting along the TPB-coated reflecting foils (right).}
\label{lightsys_pmts}
\end{figure}
\begin{figure}
\centering
\includegraphics[height=0.25\textheight]{Chapter-2/Images/lightsys_etlbase.jpeg}
\hspace{0.5cm}
\includegraphics[height=0.25\textheight]{Chapter-2/Images/lightsys_hmmbase.jpg}
\caption{\label{voltagedividers}Photos of the voltage divider bases for the ETL PMT (left) and the Hamamatsu PMT (right) used in Run-II.  The cable connections to the bases seen here were used for powering and testing prior to installation.  The yellow through-hole signal coupling capacitors seen on both bases are 18~nF (X7R) and are rated to 2~kV.}
\end{figure}
%------------------------------------------
Liquid argon scintillates in vacuum-ultraviolet (VUV) range at 128 nm; since cryogenic PMTs are not sensitive to VUV wavelengths, we need to shift the light in a region visible to the PMTs. In LArIAT, the wavelength shifting is achieved by installing on the four walls of the TPC highly-reflective VIKUITY dielectric substrate foils coated with a thin layer of tetraphenyl-butadiene (TPB) (see Figure ~\ref{lightsys_foils}). One or more visible photons  are emitted and reflected into the chamber during the interaction of a VUV photon interacts with the TPB. Thus, the light yield is increased and made more uniform across the TPC active volume, allowing the possibility of light-based calorimetry (under study).

%------------------------------------------
%\begin{figure}
%\centering
%\includegraphics[scale=1.3]{Chapter-2/Images/lightsys_foils.png}
%\caption{\label{lightsys_foils}The TPB-coated reflector foils mounted to the TPC field cage walls as viewed through the front cryostat opening. {\textcolor{red}{Better pictures needed.}}}
%\end{figure}
%------------------------------------------

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-2/Images/BeamOverview.png}
\caption{Interface of the Synoptic slow control system}
\label{fig:synoptics}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[scale=0.5]{Chapter-2/Images/BeamPosition.png}
\caption{Beam position at the upstream wire chambers monitored with ACNET.}
\label{fig:ACNET}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.6]{Chapter-2/Images/RunConditions.png}
\caption{Run Status page at LArIAT downtime. At the top the yellow bar displays the current position in the Fermilab supercycle. Interesting information to be monitored by the shifter were the run number and number of spills, time elapsed from data taking (here in red), the energy of the secondary beam and the trigger paths.}
\label{fig:runcond}
\end{figure}

@@

\begin{figure}[htb]
\centering
%\includegraphics[scale=0.6]{Chapter-2/Images/RunConditions.png}
\caption{High occupancy event display.}
\label{fig:highOcc}
\end{figure}

>>>>

%\begin{comment}     
\begin{figure}
  \centering  	
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-3/Images/AcceleratorFNAL.png}
\label{fig:Accelerator}
\caption{Layout of Fermilab Acellerator complex.}
\end{figure}

%\begin{comment}     
\begin{figure}
  \centering  	
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-3/Images/Tertiary.png}
\label{fig:tert-layout}
\caption{Birds eye view of the LArIAT tertiary beamline. In grey: upstream and downstream collimators; in yellow: bending magnets in yellow; in red: wire chambers; in blue: time of flight; in green: liquid argon TPC volume; in maroon: muon range statck.}
\end{figure}

@@

\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=3.0in]{Chapter-3/Images/ExcitationCurves.png}
\caption{
{ Magnetic field over current as a function of the current, for one NDB magnet (excitation curve). The data was collected using two Hall probes (blue and green). We fit the readings with a cubic function (black) to average of measurements (red) given in the legend.}
}
\label{fig:magnet_excitation}
\end{centering}
\end{figure}

@@

\subsection{Multi-Wire Proportional Chambers}\label{sec:MWPC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=2.3in]{Chapter-3/Images/WireChamber.png}
\caption{
{One of the four Multi Wire Proportional Chambers (WC) used in the LArIAT tertiary beamline.}
}
\label{fig:wirechamber}
\end{centering}
\end{figure}

@@

%\begin{figure}[!h]
%\begin{centering}
%\vspace{-0.3cm}
%\includegraphics[height=2.3in]{Chapter-3/Images/tofdelay.png}
%\caption{
%{\scriptsize \sf Pictures of the TOF system as was deployed during Run-I and Run-II data taking. The left image is of the upstream TOF paddle and the right image is of the downstream TOF paddle }
%}
%\label{fig:TOFSystemRunIandII}
%\end{centering}
%\end{figure}

@@

\begin{figure}[h!]
\centering
 \includegraphics[angle=90,width=0.7\textwidth]{Chapter-3/Images/Cosmic_Paddle.jpg}
\caption{Photograph of one of the scintillation counters used in the cosmic towers. } 
\label{pic:cosmicpaddle}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.18]{Chapter-3/Images/Cryostat1.jpg}
\includegraphics[scale=0.07]{Chapter-3/Images/Cryostat2.jpg}
\caption{\emph{(left)} The LArIAT cryostat open with the TPC placed in the inner volume. \emph{(right)} The LArIAT cryostat fully sealed during initial commissioning prior to installation at Fermilab Testbeam Facility.Access to the internal volume is possible by opening the upstream end caps of the inner and outer vessels. }
\label{fig:LArIATCryoStat}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{Chapter-3/Images/CryoMods.png}
\caption{Pictures of the modified components of the cryostat. $1)$ The addition of an outlet to the bottom of the cryostat to allow connections to the purification system; $2)$ The ``beam-window'' on the outer endcap and the concave inner surface of the inner endcap (referred to as the excluder) to reduce the amount of material through which beam particles must travel before entering the TPC; $3)$ The modified side port for the LArIAT light collection system.}
\label{fig:LArIATCryoMods}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{Chapter-3/Images//HVSchematic.png}\\
\caption{Schematic of the LArIAT high voltage system.}
\label{fig:HVScheme}
\end{figure}%See DocDB 1472

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{Chapter-3/Images/DriftRegions.png}\\
\caption{Schematic of the three drift regions inside the LArIAT TPC: the main drift volume between the cathode and the shield plane (C-S) in green, the region between the shield plane and the induction plane (S-I) in purple, and the region between the induction plane and the collection plane (I-C) in pink.}
\label{fig:driftregions}
\end{figure}

@@

\begin{figure}[htbp]
 \centering
 \includegraphics[width=1.0\textwidth]{Chapter-3/Images/LArIAT_FE_Electronics.png}
\caption{Overview of LArIAT Front End electronics. } 
\label{pic:FEelectronics}
\end{figure}

@@

%------------------------------------------
\begin{figure}
\centering
\includegraphics[height=2.2in]{Chapter-3/Images/lightsys_pmts.png}
\hspace{1cm}
\includegraphics[height=2.2in]{Chapter-3/Images/lightsys_wls.png}
\caption{LArIAT's photodetector system for observing LAr scintillation light inside the TPC (left), and a simplified schematic of VUV light being wavelength-shifting along the TPB-coated reflecting foils (right).}
\label{lightsys_pmts}
\end{figure}
\begin{figure}
\centering
\includegraphics[height=0.25\textheight]{Chapter-3/Images/lightsys_etlbase.jpeg}
\hspace{0.5cm}
\includegraphics[height=0.25\textheight]{Chapter-3/Images/lightsys_hmmbase.jpg}
\caption{\label{voltagedividers}Photos of the voltage divider bases for the ETL PMT (left) and the Hamamatsu PMT (right) used in Run-II.  The cable connections to the bases seen here were used for powering and testing prior to installation.  The yellow through-hole signal coupling capacitors seen on both bases are 18~nF (X7R) and are rated to 2~kV.}
\end{figure}
%------------------------------------------
Liquid argon scintillates in vacuum-ultraviolet (VUV) range at 128 nm; since cryogenic PMTs are not sensitive to VUV wavelengths, we need to shift the light in a region visible to the PMTs. In LArIAT, the wavelength shifting is achieved by installing on the four walls of the TPC highly-reflective VIKUITY dielectric substrate foils coated with a thin layer of tetraphenyl-butadiene (TPB) (see Figure ~\ref{lightsys_foils}). One or more visible photons  are emitted and reflected into the chamber during the interaction of a VUV photon interacts with the TPB. Thus, the light yield is increased and made more uniform across the TPC active volume, allowing the possibility of light-based calorimetry (under study).

%------------------------------------------
%\begin{figure}
%\centering
%\includegraphics[scale=1.3]{Chapter-3/Images/lightsys_foils.png}
%\caption{\label{lightsys_foils}The TPB-coated reflector foils mounted to the TPC field cage walls as viewed through the front cryostat opening. {\textcolor{red}{Better pictures needed.}}}
%\end{figure}
%------------------------------------------

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-3/Images/BeamOverview.png}
\caption{Interface of the Synoptic slow control system}
\label{fig:synoptics}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[scale=0.5]{Chapter-3/Images/BeamPosition.png}
\caption{Beam position at the upstream wire chambers monitored with ACNET.}
\label{fig:ACNET}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[scale=0.6]{Chapter-3/Images/RunConditions.png}
\caption{Run Status page at LArIAT downtime. At the top the yellow bar displays the current position in the Fermilab supercycle. Interesting information to be monitored by the shifter were the run number and number of spills, time elapsed from data taking (here in red), the energy of the secondary beam and the trigger paths.}
\label{fig:runcond}
\end{figure}

@@

\begin{figure}[htb]
\centering
%\includegraphics[scale=0.6]{Chapter-3/Images/RunConditions.png}
\caption{High occupancy event display.}
\label{fig:highOcc}
\end{figure}

### 2018-03-19 Chapter-7/7-BackgroundSub.tex
Changing organization structure

\chapter{Uncertainty budget}\label{ch:Uncertainty}
Measuring an hadronic cross section  in LArIAT translates into counting how many hadrons impinged on a slab of argon at a given energy and how many of those hadrons interacted at said energy. So, the key questions here are:
\begin{itemize}
\item[]a) how well do we know the kinetic energy at each point of the tracking? %(Incident Kinetic Energy bins)
\item[]b) how well do we know when the tracking stops? %(Interacting Kinetic Energy bin)
\item[]c) are there any systematic shifts?
\end{itemize}

In order to answer this question, will discuss first a simple scenario  were our beam is 100\% made of pions which arrive as primaries in the TPC (no decay in the beam and no inelastic interaction before the TPC front face). We will then add a layer of complexity by discussing how we handle beamline contamination.

\section{Pure beam of pions}
Assuming a beam of pure pions gets to the TPC, let us explicit some of the variables in the kinetic energy equation \ref{eq:KEj}  to point out the important quantities in the uncertainty budget,

\begin{align}
 E_{j}^{kin} &=  E_{Beam}^{kin}  - E_{loss} - \sum_{i < j} \frac {dE_i}{dx_i}*dx_i\\
                  &=  \sqrt{p^2_{Beam} - m^2_{Beam}} - m_{Beam} - E_{loss} - \sum_{i < j} \frac {dE_i}{dx_i}*dx_i.
\end{align}

\subsection{Uncertainty on $E_{Beam}^{kin}$}
Let us start by discussing the uncertainty on $E_{Beam}^{kin}$. Since we are assuming a beam of pions, the uncertainty on the value of mass of the pion ($m_{Beam}$) as given by the pdg is irrelevant compared to the momentum uncertainties, thus $\delta E_{Beam}^{kin} = \delta p_{Beam}^{kin}$. 
We estimate the momentum uncertainty as follows.

\textcolor{blue}{  
We estimate the uncertainty on a 4-point track. In case of 3-points track, we add an additional 2\% coming from Greg's study. 
Uncertainty on a 4-point track:
\begin{itemize}
\item[-]  Alignment surveys. 1mm misalignment translates to 3\% in overall
\item[-] Doug study dp/p = ~2\% based on field map (docdb 1710)
\item[-] Minerva test beam paper
\end{itemize}
}

\subsection{Uncertainty on $E_{loss}$}
We estimate the uncertainty on the energy loss between the beamline momentum measurement and the TPC, $E_{loss}$, using the DDMC pion sample. We shoot pions from WC4 with the same momentum distribution as in the beamline data and plot the true $E_{loss}$ for that sample. The width of the $E_{loss}$ distribution is the $\delta E_{loss}$.

\textcolor{blue}{ TO DO HERE: make sure we have the geometry right, cause otherwise this correction is meaningless.  With this method, so far we get a mean ~40 MeV, but uncertainty ~7MeV. 
The trajectory method does not improve uncertainty, why? It's a mystery I don't think we should solve before June :) .
Back of the envelope material budget calculation:}
\begin{table}[h!]
\centering
\caption{Back of the envelope calculation}
\label{my-label}
\begin{tabular}{|l|l|l|l|}
\hline
dEdx for MIP, MPV {[}MeV cm$^2$/gr{]} & density {[}g/cm$^3${]} & width {[}cm{]} & E$_{loss}$ {[}MeV{]} \\ \hline
1.6                                                 & 1.7 (G10)                            & 1.3            & 3.5                   \\
1.6                                                 & 1.4 (LAr)                            & 1.77           & 4.0                   \\
1.6                                                 & 7.7 (S.S.)                           & 0.23           & 2.8                   \\
1.6                                                 & 4.5 (Ti)                             & 0.04           & 0.3                   \\ 
1.6                                                 & 1.03 (Plastic Sci)                   & 1.1            & 1.8                   \\ \hline
Total                                               &                                      &                & 12.4                  \\ \hline
\end{tabular}
\end{table}

\textcolor{blue}{Event taking into account a 3 degree bent, we get 12.41 MeV, which is quite far from 40 MeV... something smells here ;)}

\subsection{Uncertainty on dE/dx and pitch}
We obtain the uncertainty on dE/dx and track pitch by comparing the dE/dx and pitch distributions in data and MC.
\textcolor{blue}{ Currently, MPV MC = 1.70 and MPV DATA = 1.72 MeV/cm (~3\% higher).
TO DO HERE: calculate Argon density from mid-RTD temperature. Compare this  density with MC Argon density. 
Density change  affects dE/dx (in MeV/cm!). Try changing MC density up to ``real one" and see if dEdX agrees between DATA and MC}

\subsection{Uncertainty on track end, aka efficiency correction}
From the MC, we obtain an efficiency correction on the interacting and incident distributions separately. This is done by comparing the MC reconstructed with the true MC deposition on an event by event basis.
This correction is applied bin by bin on the data interacting and incident distributions.
The better our tracking, the smaller this efficiency correction will be. So, step number one is improving the tracking.
\textcolor{blue}{Need to talk to Bruce about this.}
\textcolor{blue}{ I don't understand the angle cut that Dave Schmitz and Jon Paley were so vocal about.}

Now, the key question remains: does the tracking behave in the same way in data and MC? 
We can compare some key plots between reconstructed data and MC which gives us confidence this is true: the track pitch, the tracks straightness and the goodness of fit in data and MC. \textcolor{blue}{ Does such a variable as ``goodness of fit" exists in the tracking? We should ask Bruce.}

\section{Handling beamline contamination}
What is the beamline contamination? We define beamline contamination every TPC track matched to the WC track which is not a primary pion. There are 4 different types of beamline contaminations:
\begin{itemize}
\item[]1) electrons,
\item[]2) muons,
\item[]3) secondaries from pion events,
\item[]4) matched pile up events.
\end{itemize}

@@

Once we estimate the contaminants to primary pion ratio, the next step is subtracting their contribution from data for each type of contaminant independently. The contaminant samples are reconstructed and the corresponding interacting and incident histograms are produced. We then perform a bin by bin subtraction in the data interacting and incident histograms separately. A graphical rendering of this procedure is shown in Fig \ref{fig:backgroundSubtraction}
Once the data is background subtracted, we apply the correction laid out in the previous section.
\textcolor{blue}{How do we account for the error in the contamination subtraction? We change the electron/pion and muon/pion ratio and we see how much difference we get?}

\begin{figure}
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-8/Images/FakePlot.jpg}
\label{fig:backgroundSubtraction}
\caption{A graphical rendering of the beamline contamination background subtraction. The contribution of the contaminants is shown in green for the secondaries, in orange for the muons and in pink for electrons. The colored plots are coming from the MC and are staggered. The percentages shown in the legend are the percentages of contaminants over the total number of events  passing the selection chain. We actually expect way less contamination.}
\end{figure}

>>>>

\chapter{Background subtraction}
\section{Assessing Beamline Contamination}
What is the beamline contamination? We define beamline contamination every TPC track matched to the WC track which is not a primary pion. There are 4 different types of beamline contaminations:
\begin{itemize}
\item[]1) electrons,
\item[]2) muons,
\item[]3) secondaries from pion events,
\item[]4) matched pile up events.
\end{itemize}

@@

\section{Subtraction}
Once we estimate the contaminants to primary pion ratio, the next step is subtracting their contribution from data for each type of contaminant independently. The contaminant samples are reconstructed and the corresponding interacting and incident histograms are produced. We then perform a bin by bin subtraction in the data interacting and incident histograms separately. A graphical rendering of this procedure is shown in Fig \ref{fig:backgroundSubtraction}
Once the data is background subtracted, we apply the correction laid out in the previous section.
\textcolor{blue}{How do we account for the error in the contamination subtraction? We change the electron/pion and muon/pion ratio and we see how much difference we get?}

\begin{figure}
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-9/Images/FakePlot.jpg}
\label{fig:backgroundSubtraction}
\caption{A graphical rendering of the beamline contamination background subtraction. The contribution of the contaminants is shown in green for the secondaries, in orange for the muons and in pink for electrons. The colored plots are coming from the MC and are staggered. The percentages shown in the legend are the percentages of contaminants over the total number of events  passing the selection chain. We actually expect way less contamination.}
\end{figure}
